Differences in Homicide Case Information Indicates Why Justice is Not Served

### 2024-12-04 paper/paper.qmd
Finished paper

In @fig-ppcheckandposteriorvsprior-1, the posterior predictive check shows that the actual data follows the same curve as the posterior distribution of the fitted model and thus is consistent with it [@citetellingstories].

>>>>

In @fig-ppcheckandposteriorvsprior, the posterior predictive check shows that the actual data follows the same curve as the posterior distribution of the fitted model and thus is consistent with it [@citetellingstories].
